### 2016-04-06 Projects/DelCo_2012/Report/DelCo_2012.tex
minor edit to cafs repot

There were 7 suppression tests conducted in the two story purpose-built structure. All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over puf padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to this fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor south door. The fires were intended to replicate room and contents basement fires typically seen within residential structures. Suppression occurred at the basement double doors of the structure. Table~\ref{tab:Test_Descriptions_2} provides an overview of the suppression tests conducted.

@@

Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAFs tests conducted in the two story structure. The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 1st floor level in front of the stairway door. These values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.

>>>>

There were 7 suppression tests conducted in the two story purpose-built structure. All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to this fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor south door. The fires were intended to replicate room and contents basement fires typically seen within residential structures. Suppression occurred at the basement double doors of the structure. Table~\ref{tab:Test_Descriptions_2} provides an overview of the suppression tests conducted.

@@

Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAFs tests conducted in the two story structure. The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floor. This remote measurement location proivdes that is isolated from any direct contact from the suppression stream. The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 1st floor level in front of the stairway door. The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.
